HydroPowerModels.jl: A Julia/JuMP Package for Hydrothermal Economic Dispatch Optimization

### 2019-07-25 paper/paper.tex
target test and stop exporting plots

\begin{lstlisting}[language = Julia]
plot_grid(data, node_label=false)
\end{lstlisting}

@@

\begin{lstlisting}[language = Julia]
plot_aggregated_results(results)
\end{lstlisting}

>>>>

\begin{lstlisting}[language = Julia]
HydroPowerModels.plot_grid(data, node_label=false)
\end{lstlisting}

@@

\begin{lstlisting}[language = Julia]
HydroPowerModels.plot_aggregated_results(results)
\end{lstlisting}
